Providing better confidentiality and authentication on the Internet using Namecoin and MinimaLT

### 2014-03-29 paper.tex
New compiled paper
Fixing typo, thanks to James Vasile
https://twitter.com/jamesvasile/status/449931124064911360

\subsection{Zooko's triangle}
In this section, we are cover Zooko's triangle conjecture.

@@

\section{Confession}
This paper initially aimed at digging deeper into the crypto and protocol stuff but because of concurring deadlines I couldn't dig as deep in the MinimaLT protocol as I originally intended to.

\section{Acknowledgments}
I would like to thank everyone who provided feedback and reviewed this paper. Particularly, 
\begin{itemize}
\item Greg Slepak who is currently working on the DNSNMC implementation and author of the OkTurtles\cite{okTurtles} paper for providing very valuable feedback to improve this paper.
\item All folks from Noisy Square at \#30c3 for the insightful discussions that influenced this paper.
\item Dylan Bourgeois, a friend of mine, for spotting so many typos.
\end{itemize}

>>>>

\subsection{Zooko's triangle}
In this section, we are covering Zooko's triangle conjecture.

@@

\section{Acknowledgments}
I would like to thank everyone who provided feedback and reviewed this paper. Particularly, 
\begin{itemize}
\item Greg Slepak who is currently working on the DNSNMC implementation and author of the OkTurtles\cite{okTurtles} paper for providing very valuable feedback to improve this paper.
\item All folks from Noisy Square at \#30c3 for the insightful discussions that influenced this paper.
\item Dylan Bourgeois, a friend of mine, for spotting so many typos.
\item Romain Ruetschi, another friend, for fixing a lot of my grammar mistakes.
\end{itemize}
